\documentclass[11pt,smallheadings,parskip]{scrartcl}
\usepackage{/Users/kaie/Documents/tex/sty/dataref,folsynt}
\usepackage{amsmath,deflist,url,natbib}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\title{Errata for \citep{EdR:cup98}}
\author{Kai Engelhardt}
% \date{Version 1}
\begin{document}
\maketitle
Typos are indexed in the format
$\langle\text{\textit{pagenumber}}\rangle:[+|-]\langle\text{\textit{linecount}}\rangle$,
where a minus-sign indicates that line counting starts at the bottom
of the page.

\begin{deflist}{MMM}
\item[x:-12] The old URL for this book hosted in Kiel is dead. A correct URL for the book web site is \url{https://doi.org/10.1017/CBO9780511663079} which currently resolves to its homepage at the publisher. Sadly the publisher doesn't host this list.
\item[35:-5] ``\itext{cons}'' should be ``\cons''.
\item[38:+3] omit hyphen between ``value'' and ``returned''.
\item[57:+14] ``$S(P)$'' should be ``$P(S)$''.
\item[79:+4] ``$(\xi,\xi)$'' should be ``$(\tau,\xi)$''.
\item[96:-6] insert ``$\sigma$'' after ``$\Tsem p$''.
\item[99:+1] ``$\tau$'' is missing at the end of the line.
\item[100:+3] ``$e$'' should be ``$e_1$''.
\item[101:-3] spelling ``straightfo\textbf{rw}ard''
\item[105:-14] spelling ``di\textbf{s}cussion''
\item[118:+10]  ``Hence, there is no such $\sigma^{(i)}$'' could be a bit terse. It might help to insert ``The existence of such a $\sigma^{(i)}$ contradicted the requirement stated above, namely, that $(\sigma^{(i)},\sigma^{(i+2)})$ should not be contained in $\Psem{\phi\leadsto\psi}\A$.'' before.
\item[120:+8] insert ``the remaining parts of'' after ``5.5\quad Prove''.
\item[121:+4] should be
  \begin{gather*}
    \Htri{x<17}{x+3=x_0 \leadsto x<x_0}{%
      \Exi{y_0}{%
        y_0<17 \And \All{x_0}{%
          y_0+3=x_0 \Implies x<x_0}}}
  \end{gather*}
  that is, there's no role for vectors in this example because there's
  only one variable of each kind to begin with.
\item[121:+6] ``$x<20$'' should be ``$x<19$'' since we're going through two $<$.
\item[136:+11] the postcondition of the specification statement should be ``$(b,x = b_0 \bagplus x_0,x_0)$''.
\item[151:-8] ``$\bot_a$'' should be ``$\bot_A$''.
\item[153:+1] ``on proves'' should be ``one proves''.
\item[153:-14] ``$i\in\nat$'' should be ``$i\in I$''.
  % and one might add that $I$ is $k$'s domain
\item[321:+7] ``$b' = b\oplus x$'' should be ``$b' = b\oplus x?$''.
\item[322:-1] ``quantification over all the schema’s variables'' is not complete, as the predicate should also be included. So the example in the first line of page 323 becomes:
\input{cheapfuzz}
\begin{zed}
  \forall \NonEmptyBagC @ P \iff\\
  \forall \Vsum : \zReal; n : \nat; \elements : \nat @
  (((n=0) \implies (\Vsum=0)) \land n < \elements \land  n \neq
  0)\implies P
\end{zed}
\item[364:-15] ``$\Htri\kappa{S_1}\rho$'' should be ``$\Htri\kappa{S_2}\rho$''.
\item[364:-4] drop ``the'' between ``case'' and ``of''.
  %% can't find this:
  % \item[390:+12] $c(c[i])$ should be $c[c[i]]$
\end{deflist}
Thanks to Eerke Boiten, Ulrich Hannemann, Wolfgang Hielscher, and Ronald Kriemann for pointing out errors.
\bibliographystyle{plainnat}
\bibliography{strings,kai}
\end{document}
